---
output:
  html_document:
    highlight: tango
    self_contained: true
    theme: null
    css: style.css
---
# String Manipulation for Tidying Text Data
## Requirements

```{r}
library(stringr)
```

## Text Length Measurement with `str_length()`

```{r}
str_length(c("a", "banana", NA))
```

## String Concatenation with `str_c()`

```{r}
str_c("x", "y")
str_c("x", "y", "z")
str_c("x", "y", "z", sep=",")
```

### Checking Regular Expressions

```{r}
str_c("Letter: ", letters)
```

### Handling NAs

```{r}
x <- c("abc", NA)
str_c("|-", x, "-|")
str_c("|-", str_replace_na(x), "-|")
```

### Exercises

```{r}
str_c(c("a", NA, "b"), "-d")

y <- c("a", NA, "b")

z <- str_c(c(y), "-d")
z

z <- str_c(c("a", NA, "b"), "-d")
z

str_c(str_replace_na(y), "-d")
```

### Practice: Interactive Web Page Message Implementation

```{r}
name <- "David"
time <- "morning"
str_c("Good", " ", time, ",", " ", name, "!")

bday <- FALSE
bday <- TRUE
str_c("Good", " ", time, ",", " ", name, if (bday) " and Happy Birthday", "!")
```

## Substring Extraction with `str_sub()`

```{r}
hw <- "Hadley Wickham"
str_sub(hw, 1, 6)
str_sub(hw, end=6)
str_sub(hw, 8, 14)
str_sub(hw, 8)
str_sub(hw, -1)
str_sub(hw, -7)
```

### Exercises

```{r}
x <- c("apple", "banana", "Pear")
str_sub(x, 1, 3)
str_sub(x, 3)
str_sub(x, -3)
str_sub(x, -3, -2)
str_sub(x, end=-3)
```

## Pattern Matching with `str_view()`

```{r}
x <- c("blur", "oasis", "libertines")
str_view(x,"b")
str_view(x,"^o")
str_view(x, "s$")
str_view(x, "[oab]")
str_view(x, "..")
```

### Exercises

```{r}
# Matches any single character listed inside []
str_view(c("abc", "def", "fghi"), "[aeiou]")

# .. matches any two consecutive characters
str_view(c("abc", "def", "fghi"), "..")

# Displays only strings containing "e"
str_view(c("abc", "def", "fghi"), "e")

# Displays all strings; highlights matches for "e"
str_view(c("abc", "def", "fghi"), "e", match=NA)

# Displays only strings that do not contain "e"
str_view(c("abc", "def", "fghi"), "e", match=FALSE)
```

### Regular Expression Quantifiers
- `{2}`: precisely two characters
- `{n,}`: n or more characters
- `{,m}`: at most m characters
- `{n,m}`: between n and m characters

```{r}
str_view(words, "e{2}")
str_view(words, "e{1,}")
str_view(words, "e{0,1}")
```

### Practice: Identifying Matching Patterns

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
str_view(x, "^a")
str_view(x, "a$")

y <- c("apple pie", "apple", "apple cake")
str_view(y, "apple")
str_view(y, "^apple$")

str_view(c("abc", "def", "fghi"), "[aeiou]")
str_view(c("abc", "def", "fghi"), "..")
str_view(c("abc", "def", "fghi"), "..$")
str_view(c("abc", "def", "fghi"), "e")
```

### Practice: Handling Quotation Marks

```{r}
Str1 <- "This is a string"
Str2 <- 'If I want to include a "quote" inside a string, I use single quotes'
```

## Pattern Filtering with `str_subset()`

```{r}
str_subset(words, "^.{3}$")
str_subset(words, "^y")
str_subset(words, "x$")
str_subset(words, "^.{7}")
```

### Exercises

```{r}
# Matches words consisting of exactly three characters
str_subset(words, "^.{3}$")
```

### Regular Expression Quantifiers
- `*`: zero or more times
- `+`: one or more times
- `?`: zero or one time

```{r}
Regex_ex <- c("apple", "banana", "bat", "ant", "z", "aa", "ab", "a", "b", "")

# Matches strings starting with "a", followed by zero or more characters
str_subset(Regex_ex, "^a.*")
# Matches strings starting with "a", followed by one or more characters
str_subset(Regex_ex, "^a.+")
# Matches strings starting with "a", followed by zero or one character
str_subset(Regex_ex, "^a.?")
# Matches strings starting with "a", followed by zero or one character, with no further characters
str_subset(Regex_ex, "^a.?$")

# Matches words consisting of exactly three characters
str_subset(words, "^.{3}$")
# Matches words beginning with at least three characters (no upper limit)
str_subset(words, "^.{3}")

# Matches words consisting of two to four characters
str_subset(words, "^.{2,4}$")
```

### Practice: Detecting Proper Nouns

```{r}
# Matches strings beginning with an uppercase letter
str_subset(words, "^[A-Z].*$")
str_subset(words, "^[A-Z].*")

# Matches words beginning with "y"
str_subset(words, "^y")
# Matches words beginning with "y" followed by exactly one character
str_subset(words, "^y.")
# Matches words beginning with "y" followed by zero or more characters
str_subset(words, "^y.*")

# Matches words ending with "x"
str_subset(words, "x$")

str_subset(words, "^.{3}$")
str_subset(words, "^...$")
```

## Practice: Searching Words with Seven or More Characters

```{r}
str_subset(words, "^.{7}.*$")
str_subset(words, "^.{7,}$")
str_subset(words, "^.......")

# Invalid: nothing follows "^" before the quantifier
# str_subset(words, "^{,7}.$")
# 
# Invalid: "{,m}" requires a preceding element to quantify
# str_subset(words, "^.{,7}.$")
# 
# Invalid: "{,m}" is not supported in R's default regex engine
# str_subset(words, "^.{,7}$")
# 
# Invalid: same issue as above
# str_subset(words, "^.{,7}")

# Valid syntax, but does not produce the intended result
# a minimum bound should be specified for clarity
str_subset(words, "^.{1,7}.$")
```

